R-LIME: LIME法における矩形制約と最適化

### 2024-04-08 paper/paper.tex
ICPR 6th version
modify details of paper

\ifnum\mode=0
  \pagestyle{plain}
  \pagenumbering{roman}
  \tableofcontents
  \newpage
  \listoffigures\listoftables\clearpage
  \AddToHook{cmd/section/before}{\clearpage}
  \pagestyle{plain}
  \pagenumbering{arabic}
\else
  % The abstract should briefly summarize the contents of the paper in
  % 150--250 words.
  \begin{abstract}
    In recent years,
    complex machine learning models have been introduced
    in various industrial fields due to their high accuracy.
    However,
    their complexity has been a major obstacle to implementation
    in sensitive decision-making situations.
    In order to address this problem,
    various post-hoc explanation methods have been proposed,
    but they have not been able to achieve interpretability of
    both the explanation and its scope.
    We propose a new method, R-LIME,
    which interprets complex classifiers in an interpretable scope.
    R-LIME locally approximates a decision boundary of a black-box classifier
    in a rectangular region
    and maximizes the region as long as the accuracy of the linear
    classifier is higher than a given threshold.
    The resulting rectangular region is interpretable for users because it is
    expressed as a conjunction of feature predicates.
    Comparing R-LIME with the existing method,
    we demonstrate the effectiveness of the proposed method through qualitative
    and quantitative experiments using a real-world dataset.
    % 150 words
    \keywords{Interpretable machine learning \and Local surrogate model}
  \end{abstract}
\fi

\section{Introduction}
Machine learning models, such as deep learning and random forests,
have been widely employed in various industrial applications
due to their significant improvement in accuracy in recent years.
However,
the increasing complexity and black-box nature of these models pose challenges,
particularly in critical decision-making scenarios like healthcare and finance,
where the opacity of decision process becomes a major obstacle to
implementation.
Consequently,
there has been extensive research in the field of post-hoc explanations
for machine learning models~\cite{%
  guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
Existing post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure.
Furthermore, model-agnostic methods are classified into
\emph{global} and \emph{local} methods based on their locality in input space.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \ifnum\mode=0
      \vspace{-1.79cm}
    \else
      \vspace{-2.24cm}
    \fi
    \includegraphics[scale=\scale]{example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method).
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

In this paper,
we focus on local model-agnostic methods.
An example of explanations by LIME~\cite{ribeiro2016why} and
Anchor~\cite{ribeiro2018anchors}
for a sentiment prediction model is illustrated in \cref{fig:example}.
LIME approximates the complex decision boundary
linearly around the given focal point,
then provides the weights of the linear model as the contribution of each feature
to the output.
The explanation by LIME (\cref{fig:example-lime}) provides suggests that
the word ``not'' mainly contributes to the positive prediction,
but does not explicitly indicate the effective scope.
Without the scope,
users might mistakenly apply the knowledge derived from the explanation
to other instances far from the focal point,
potentially leading to misunderstanding of the black-box model's behavior
\cite{ribeiro2018anchors}.
For this example,
user may apply the derived insights
to the sentence ``This book is not good.''
and mistakenly conclude that the word ``not''
mainly contributes to the positive prediction for this sentence as well,
which is obviously incorrect.
Anchor represents a rectangular region
containing the focal point,
that maximizes the probability of the black-box classifier outputting
the same label as the focal point.
While Anchor provides an effective scope of the explanation,
the information it includes is less than LIME,
limiting its utility~\cite{ribeiro2018anchors}.
The explanation by Anchor (\cref{fig:example-anchor})
suggests that changing words other than ``not'' and ``bad''
has little impact on the classifier's output.
While it clearly cannot be applied to the sentence ``This book is not good''
because of not including the word ``bad'',
the explanation does not provide details about the influence of each word,
resulting in less user insight into the model's behavior compared to LIME.

To address this limitation of LIME,
we propose a new method called R-LIME (Ruled LIME),
which interprets complex classifiers in an interpretable region.
R-LIME locally approximates a complex decision boundary linearly
in a rectangular region and maximizes the region
as long as the accuracy of the linear classifier is
higher than a given threshold.
The rectangular region is interpretable for users because it is
expressed as a conjunction of feature predicates (\cref{fig:example-rlime}).
An example of the explanation by R-LIME for a sentiment prediction model
is illustrated in \cref{fig:example-rlime}.
It is clear that users can apply the insights derived from the explanation
only to the sentences containing the word ``not''.

\section{Related Work}
\begin{figure}[tbp]
  \centering
  \def\w{2.2}
  \def\ww{4.4}
  \def\h{0.7}
  \def\hh{1.4}
  \def\hhh{2.1}
  \def\hhhh{2.8}
  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
    \node[nodestyle] (dependent) at (-\w,-\hh){%
      \begin{tabular}{c}
        model-dependent \\
        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
      \end{tabular}
    };
    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
    \node[nodestyle] (global) at (0,-\hhhh){%
      \begin{tabular}{c}
        global \\
        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
      \end{tabular}
    };
    \node[nodestyle] (local) at (\ww,-\hhhh){%
      \begin{tabular}{c}
        \textbf{local} \\
        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors})
      \end{tabular}
    };
    \draw(post-hoc) -- (0,-\h);
    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
    \draw(agnostic) -- (\w,-\hhh);
    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
  \end{tikzpicture}
  \caption{%
    Categorization of post-hoc explanation methods.
    We focus on \emph{model-agnostic} and \emph{local} methods,
    which explain model's local behavior using only its output.
  }\label{fig:post-hoc}
\end{figure}
In this section,
we overview existing research on post-hoc explanation methods,
which explain the behavior of black-box models already trained.
As shown in \cref{fig:post-hoc},
post-hoc methods are classified into several categories.

@@

Furthermore, model-agnostic methods are categorized into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods,
such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
% seeking explanations valid for any input.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as Local Interpretable Model-agnostic Explanations (LIME)
\cite{ribeiro2016why}
and Anchor~\cite{ribeiro2018anchors},
% SHAP~\cite{lundberg2017unified},
% EXPLAN~\cite{rasouli2020explan},
% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
% and BELLA (Black box model Explanations by Local Linear Approximations)
% \cite{radulovic2023bella},
explain model's behavior in the vicinity of a specific input.
While local methods offer explanations more simple and accurate
than global methods,
the scope of the explanation is limited locally.

\section{Proposed Method}
\begin{figure}[tbp]
  \centering
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-lime}
    \caption{%
      LIME: Locally approximates the decision boundary around the focal point.
    }\label{fig:lime}
  \end{subfigure}%
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-anchor}
    \caption{%
      Anchor: Maximizes coverage of a rectangular region
      containing the focal point under accuracy constraints.
    }\label{fig:anchor}
  \end{subfigure}
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-rlime3}
    \caption{%
      R-LIME:
      Maximizes coverage of a rectangular region
      under lower constraints on the accuracy of the linear classifier.
    }\label{fig:rlime}
  \end{subfigure}
  \caption[Visual comparison of LIME, Anchor and R-LIME]{%
    Visual comparison of LIME, Anchor and R-LIME (our proposed method).
    The solid line represents the rectangular region containing the focal
    point, and the dashed line represents the learned approximation model.
  }
\end{figure}

@@

\subsubsection[Anchor]{%
  Anchor~\cite{ribeiro2018anchors}
}\label{sec:anchor}
Anchor represents a rectangular region containing the focal point $x$,
expressed as a conjunction of feature predicates (a rule),
that maximizes the probability of the black-box classifier $f$
outputting $f(x)$ within the region.
It aims to highlight important features
contributing significantly to the output (\cref{fig:anchor}).
For a discrete $m$-dimensional input space $\ispace$
with a trained black-box classifier $f: \ispace \to \{0,1\}$,
an instance $x \in \ispace$,
and a distribution $\mathcal{D}$ over the input space,
a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
\begin{align}
  \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)].
\end{align}
where $\mathcal{D}(z|A)$ is the conditional distribution in the region
where the rule $A$ returns true.
$\Prec(A)$ represents the probability that the output of $f$ matches
between the perturbation $z\sim\mathcal{D}(z|A)$ and the focal point $x$,
and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
Anchor maximizes coverage under the constraint that
the accuracy of the rule $A$ exceeds a given threshold $\tau$.
However, \cref{eq:anchor_def_prec} is not directly computable.
Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$,
the accuracy constraint is relaxed as follows:
\begin{equation}
  \label{eq:const_prec}
  P(\Prec(A)\ge\tau)\ge1-\delta.
\end{equation}
Thus, the following optimization problem is solved:
\begin{equation}
  \label{eq:main_problem}
  A^*=\underset{A \text{~s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
  {\arg\max}\Cov(A).
\end{equation}

@@

  For each iteration of KL-LUCB algorithm, R-LIME needs to update
  the linear classifier $g_i$, which is not required in Anchor.
  But if we use logistic regression as the linear classifier,
  the computational complexity of updating $g_i$ is $\mathcal{O}(m)$,
  which is negligible compared to the complexity of sampling a perturbation vector
  and getting the output of the black-box model.
\fi

>>>>

\ifnum\mode=0
  \pagestyle{plain}
  \pagenumbering{roman}
  \tableofcontents
  \newpage
  \listoffigures\listoftables\clearpage
  \AddToHook{cmd/section/before}{\clearpage}
  \pagestyle{plain}
  \pagenumbering{arabic}
\else
  % The abstract should briefly summarize the contents of the paper in
  % 150--250 words.
  \begin{abstract}
    In recent years,
    complex machine learning models have been introduced
    in various industrial fields due to their high accuracy.
    However,
    their complexity has been a major obstacle to implementation
    in sensitive decision-making situations.
    In order to address this problem,
    various post-hoc explanation methods have been proposed,
    but they have not been able to achieve interpretability of
    both the explanation and its scope.
    We propose a new method, R-LIME,
    which interprets a complex classifier in an interpretable scope.
    R-LIME locally approximates a decision boundary of a black-box classifier
    in a rectangular region
    and maximizes the region as long as the accuracy of the linear
    classifier is higher than a given threshold.
    The resulting rectangular region is interpretable for users because it is
    expressed as a conjunction of feature predicates.
    We demonstrate the effectiveness of the proposed method through
    qualitative and quantitative comparisons with the existing method
    using a real-world dataset.
    % 150 words
    \keywords{Interpretable machine learning \and Local surrogate model}
  \end{abstract}
\fi

\section{Introduction}
Machine learning models, such as deep neural networks and random forests,
have been widely introduced in various industrial fields
due to their significant improvement in accuracy in recent years.
However,
the increasing complexity and black-box nature of these models pose challenges,
particularly in critical decision-making scenarios such as healthcare and finance,
where the opacity of decision process becomes a major obstacle to implementation.
In order to address this problem,
there has been extensive research in the field of post-hoc explanations
for machine learning models~\cite{%
  guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
Existing post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure,
and the latter are further classified into \emph{global} and \emph{local} methods
based on their locality in input space~\cite{samek2021explaining}.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \ifnum\mode=0
      \vspace{-1.79cm}
    \else
      \vspace{-2.24cm}
    \fi
    \includegraphics[scale=\scale]{example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method).
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

In this paper,
we focus on \emph{local} and \emph{model-agnostic} methods.
LIME~\cite{ribeiro2016why} and Anchor~\cite{ribeiro2018anchors}
are representative local model-agnostic methods.
An example of explanations by LIME and Anchor
for a sentiment prediction model is illustrated in \cref{fig:example}.
LIME approximates the complex decision boundary
linearly around the given focal point,
then provides the weights of the linear model as the contribution of each feature
to the output.
The explanation by LIME (\cref{fig:example-lime}) suggests that
the word ``not'' mainly contributes to the positive prediction,
but does not explicitly indicate the effective scope.
Without the scope,
users might mistakenly apply the knowledge derived from the explanation
to other instances far from the focal point,
potentially leading to misunderstanding of the black-box model's behavior
\cite{ribeiro2018anchors}.
For this example,
user may apply the derived insights
to the sentence ``This book is not good.''
and mistakenly conclude that the word ``not''
mainly contributes to the positive prediction for this sentence as well,
which is obviously incorrect.
Anchor maximizes the coverage of a rectangular region containing the focal point
as long as the probability of the black-box classifier outputting
the same label as the focal point within the region exceeds a given threshold.
While Anchor provides an effective scope of the explanation,
users can get less insight from the explanation compared to LIME\@.
The explanation by Anchor (\cref{fig:example-anchor})
suggests that replacing words other than ``not'' and ``bad''
has little impact on the classifier's output.
While it clearly cannot be applied to the sentence ``This book is not good''
because of not including the word ``bad'',
the explanation does not provide details about the influence of each word,
resulting in less user insight into the model's behavior compared to LIME.

To address this limitation of LIME,
we propose a new method called R-LIME (Ruled LIME),
which provides both the contributions of each feature to the output
and the effective scope of the explanation.
R-LIME locally approximates a complex decision boundary linearly
in a rectangular region and maximizes the region
as long as the accuracy of the linear classifier exceeds a given threshold.
The rectangular region is interpretable for users because it is
expressed as a conjunction of feature predicates.
An example of the explanation by R-LIME for a sentiment prediction model
is illustrated in \cref{fig:example-rlime}.
It is clear that users can apply the insights derived from the explanation
only to the sentences containing the word ``not''.

\section{Related Work}
\begin{figure}[tbp]
  \centering
  \def\w{2.5}
  \def\ww{5.0}
  \def\h{0.7}
  \def\hh{1.4}
  \def\hhh{2.1}
  \def\hhhh{2.8}
  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
    \node[nodestyle] (dependent) at (-\w,-\hh){%
      \begin{tabular}{c}
        model-dependent \\
        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
      \end{tabular}
    };
    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
    \node[nodestyle] (global) at (0,-\hhhh){%
      \begin{tabular}{c}
        global \\
        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
      \end{tabular}
    };
    \node[nodestyle] (local) at (\ww,-\hhhh){%
      \begin{tabular}{c}
        \textbf{local} \\
        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors}, \underline{R-LIME})
      \end{tabular}
    };
    \draw(post-hoc) -- (0,-\h);
    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
    \draw(agnostic) -- (\w,-\hhh);
    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
  \end{tikzpicture}
  \caption{%
    Categorization of post-hoc explanation methods.
    We focus on \emph{model-agnostic} and \emph{local} methods,
    which explain model's local behavior using only its output.
  }\label{fig:post-hoc}
\end{figure}
In this section,
we overview existing research on post-hoc explanation methods,
which explain the behavior of black-box models already trained.
As shown in \cref{fig:post-hoc},
post-hoc methods are classified into several categories.

@@

Furthermore, model-agnostic methods are categorized into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods,
such as Partial Dependence Plots (PDP)~\cite{friedman2001greedy}
and Accumulated Local Effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
% seeking explanations valid for any input.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as Local Interpretable Model-agnostic Explanations (LIME)
\cite{ribeiro2016why}
and Anchor~\cite{ribeiro2018anchors},
% SHAP~\cite{lundberg2017unified},
% EXPLAN~\cite{rasouli2020explan},
% LORE (Local Rule-based Explanations)~\cite{guidotti2018local}
% and BELLA (Black box model Explanations by Local Linear Approximations)
% \cite{radulovic2023bella},
explain model's behavior in the vicinity of a specific input.
While they offer explanations more simple and accurate
than global methods,
the scope of the explanation is limited locally.

\section{Proposed Method}
\begin{figure}[tbp]
  \centering
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-lime}
    \caption{%
      LIME: Locally approximates the decision boundary around the focal point.
    }\label{fig:lime}
  \end{subfigure}%
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-anchor}
    \caption{%
      Anchor: Maximizes coverage of a rectangular region
      containing the focal point under accuracy constraints.
    }\label{fig:anchor}
  \end{subfigure}
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-rlime3}
    \caption{%
      R-LIME:
      Maximizes coverage of a rectangular region
      under lower constraints on the accuracy of the linear classifier.
    }\label{fig:rlime}
  \end{subfigure}
  \caption[Visual comparison of LIME, Anchor and R-LIME]{%
    Visual comparison of LIME, Anchor and R-LIME (our method).
    The dashed line represents the learned approximation model,
    and the solid line represents the rectangular region containing the focal point.
  }
\end{figure}

@@

\subsubsection[Anchor]{%
  Anchor~\cite{ribeiro2018anchors}
}\label{sec:anchor}
Anchor maximizes the coverage of a rectangular region
containing the focal point $x$,
expressed as a conjunction of feature predicates (a rule)
as long as the probability of the black-box classifier $f$
outputting $f(x)$ within the region exceeds a given threshold $\tau$
(\cref{fig:anchor}).
It aims to highlight important features
contributing significantly to the output.
For a discrete $m$-dimensional input space $\ispace$,
a trained black-box classifier $f: \ispace \to \{0,1\}$,
an instance $x \in \ispace$
and a distribution $\mathcal{D}$ over the input space,
a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
The predicate $a_i(z)$ evaluates to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
\begin{align}
  \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)],
\end{align}
where $\mathcal{D}(z|A)$ is the conditional distribution in the region
where the rule $A$ returns true.
$\Prec(A)$ represents the probability that the output of $f$ matches
between the perturbation $z\sim\mathcal{D}(z|A)$ and the focal point $x$,
and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
Anchor maximizes coverage under the constraint that
the accuracy of the rule $A$ exceeds a given threshold $\tau$.
However, \cref{eq:anchor_def_prec} is not directly computable.
Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$,
the accuracy constraint is relaxed as follows:
\begin{equation}
  \label{eq:const_prec}
  P(\Prec(A)\ge\tau)\ge1-\delta.
\end{equation}
Thus, the following optimization problem is solved:
\begin{equation}
  \label{eq:main_problem}
  A^*=\underset{A \text{~s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
  {\arg\max}\Cov(A).
\end{equation}

@@

  For each iteration of KL-LUCB algorithm, R-LIME needs to update
  the linear classifier $g_i$, which is not required in Anchor.
  But if we use logistic regression as the linear classifier,
  the computational complexity of updating $g_i$ is $\mathcal{O}(m)$,
  which is negligible compared to the complexity of sampling a perturbation vector
  and getting the output of the black-box model.
  Overall, the computational complexity of R-LIME is comparable to that of Anchor.
\fi
